\documentclass[12pt]{article}

\usepackage{fullpage,amsmath,amssymb,amsthm}

\newcommand{\D}{\displaystyle}

\title{Math 199 CD2: Midterm 3 review}
\date{\today}


\begin{document}
	
	\maketitle
	\section{Related Rates}
	\begin{enumerate}
		\item A Ferris wheel with a radius of 15 m is rotating at a rate of one revolution every two minutes. Exactly how fast (in m/min) is a rider rising when his seat is 27 m above ground level?
		\vskip 4cm
		
		\item A 5-foot girl is walking toward a 20-foot lamppost at the rate of 6 feet per second. How fast is the tip of her shadow (cast by the lamp) moving?
		\vskip 5cm
		\newpage
		\item A small funnel in the shape of a cone is being emptied of fluid at the rate of 12cubic centimeters per second. The height of the funnel is 20 centimeters and the radius of the top is 4 centimeters. How fast is the fluid level dropping when the level stands 5 centimeters above the vertex of the cone?
		\vskip 7cm
		\item A particle moves on the hyperbola $x^2 - 18y^2 = 9$ in such a way that its $y$-coordinate increases at a constant rate of 9 units per second. How fast is its $x$-coordinate changing when $x = 9$?
		\vskip3cm
	\end{enumerate}
	\section{Log/Exp differentiation}
	\begin{enumerate}
	
		\item Find the derivative of the following function:
		\begin{enumerate}
			\item $y=x^x$\vskip 3cm
			\item $y=(4x+1)^{5x}$\vskip 3cm
			\item $y=x^{x^2+4}$\vskip 3cm
		\end{enumerate}
	\end{enumerate}
	\section{Rolle's Theorem, MVT, IVT}
	Please state all 3 theorem before you even attempt\\
	
	Consider the polynomial $f(x) = 5x^3 - 2x^2 +3x -4$. Prove that $f(x)$ has a zero between $0$ and $1$ that is the only zero of $f(x)$.
	\vskip 6cm

	\section{Exponential Growth or Decay}
	\begin{enumerate}
		\item A certain chemical decomposes exponentially. Assume that 200grams becomes 50 grams in 1hour. How much
		will remain after 3 hours?
		\vskip 3cm
		\item If the world population in 1980 was 4.5 billion and if it is growing exponentially with a growth constant
		$K = 0.04 \ln 2$, find the population in the year 2030.
		\vskip 3cm
		\item Fruit flies are being bred in an enclosure that can hold a maximum of 640 flies. If the flies multiply exponentially, with a growth constant $K = 0.05$ and where time is measured in days, how long will it take an initial population
		of 20 to fill the enclosure?
		\vskip 4cm
		\item A bacterial culture, growing exponentially, increases from 100 to 400grams in 10 hours. How much was present
		after 3 hours?
	\end{enumerate}
\end{document}