\documentclass{article}

\usepackage{fullpage,amsmath,amssymb,amsthm,graphicx}

\title{Math 199 CD2: Review and More on Derivative}
\date{Spetember 15, 2021}
\pagenumbering{gobble}

\begin{document}

\maketitle

\section{Review}
\subsection{Limit}

 For what value of $k$ is the following a continuous function?\\
	$$f(x)=\begin{cases}
		\frac{\sqrt{7x+2}-\sqrt{6x+4}}{x-2} & \text{if \ $x \geq -2/7$\ and \ $x\neq 2$} \\
		k & \text{if \ $x=2$}
	\end{cases}$$
\vskip 5cm
\subsection{$\epsilon$-$\delta$}
\begin{enumerate}
	\item Given $\epsilon=1$, what can $\delta$ be for the following expression: 
	$$\lim_{x \to 1} 9x+10=19$$
	It's better if you start writing out the $\epsilon-\delta$ definition of this limit first
	\vskip 5cm
	
	\item Given $\epsilon=0.5$, what can $\delta$ be for the following expression: 
	$$\lim_{x \to 1/2} x+10=21/2$$
	\item Ask me if you still want more practice so I can give it to you
\end{enumerate}



\section{Product Rule}
\begin{enumerate}

\item \textbf{More Products.} In this problem we will extend the product rule to apply to the product of two or more functions.

\begin{enumerate}

\item Write $\frac{d}{dx}(f(x)g(x))$ in terms of $f$, $g$, and their derivatives.


\vskip 4cm

\item Write $\frac{d}{dx}(f(x)g(x)h(x))$ in terms of $f$, $g$, $h$ and their derivatives.

\vskip 4cm
\item Describe how to calculate $\frac{d}{dx} (f_1(x) f_2(x) \cdots f_n(x))$.

\vskip 7cm

\item Using the rule above, calculate $\frac{d}{dx} (f(x)^n)$ for $n \geq 1$ (without using the chain rule!).


\vskip 4cm

\end{enumerate}

\item \textbf{More Derivatives.} In this problem, we will extend the product rule to more derivatives.

\begin{enumerate}

\item Write $\frac{d}{dx} (f(x)g(x))$ in terms of $f$, $g$, and their derivatives.


\vskip 4cm
\item Write $\frac{d^2}{dx^2} (f(x)g(x))$ in terms of $f$, $g$, and their derivatives.


\vskip 4cm




\item Expand $(x+y)^2$, $(x+y)^3$, and $(x+y)^4$ and compare to the above.


\vskip 4cm
\item Let $f(x) = x^n e^x$. Find $f^{(n)}(0)$.


\vskip 4cm

\end{enumerate}


\end{enumerate}

\end{document}
